Bayesian multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-06-26 manuscript/manuscript.tex
section 3

%  ALWAYS USE THE referee OPTION WITH PAPERS SUBMITTED TO BIOMETRICS!!!
%  You can see what your paper would look like typeset by removing
%  the referee option.  Because the typeset version will be in two
%  columns, however, some of your equations may be too long. DO NOT
%  use the \longequation option discussed in the user guide!!!  This option
%  is reserved ONLY for equations that are impossible to split across 
%  multiple lines; e.g., a very wide matrix.  Instead, type your equations 
%  so that they stay in one column and are split across several lines, 
%  as are almost all equations in the journal.  Use a recent version of the
%  journal as a guide. 
%  
\documentclass[useAMS,referee]{biom}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{booktabs}
\usepackage{breqn}
\usepackage{algorithm}
\usepackage{algcompatible}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{dsfont}
\usepackage{amsfonts}

@@

\begin{abstract}
In studies of infant motor development, a crucial research goal is to identify latent clusters of infants that experience delayed development, as this is a known risk factor for adverse outcomes later in life. However, there are a number of statistical challenges in modeling infant development: the data are typically skewed, exhibit intermittent missingness, and are highly correlated across the repeated measurements collected during infancy. Using data from the Nurture study, a cohort of over 600 mother-infant pairs followed from pregnancy to 12 months postpartum, we develop a flexible Bayesian latent class model for the analysis infant motor development. Our model has a number of attractive features. First, we adopt the multivariate skew normal distribution with cluster-specific parameters that accommodate the inherent correlation and skewness in the data. Second, we model the cluster membership probabilities using a novel Pólya-Gamma data-augmentation scheme, thereby improving predictions of the cluster membership allocations. Lastly, we impute missing responses under missing at random assumption by drawing from appropriate conditional skew normal distributions. Bayesian inference is achieved through straightforward Gibbs sampling, and can be carried out in available software such as R.  Through simulation studies, we show that the proposed model yields improved inferences over models that ignore skewness. In addition, our imputation method yields improvements compared to conventional missing data methods, including multiple imputation and complete or available case analysis. When applied to Nurture data, we identified two distinct development clusters: one characterized by delayed “U-shaped” development and a higher percentage of male infants and another characterized by more steady development and a lower percentage of males. The clusters also differed in terms of key demographic variables, such as infant race and maternal pre-pregnancy body mass index. These findings can aid investigators in targeting interventions during this critical early-life developmental window.
\end{abstract}

@@

@@

\subsubsection{Prior Specification}
We adopt a fully Bayesian inferential approach and assign prior distributions to all model parameters. Conveniently, all parameters admit conditionally conjugate priors, which greatly improves posterior computation via a data-augmented Gibbs sampler. For the MSN model component, we adopt a conditionally independent prior structure for $\boldsymbol\beta_k$ and $\boldsymbol\Sigma_k$, where $p(\boldsymbol\beta_k,\boldsymbol\Sigma_k) = p(\boldsymbol\Sigma_k)p(\boldsymbol\beta_k|\boldsymbol\Sigma_k)$. We choose the normal-inverse-Wishart distribution for $p(\boldsymbol\beta_k,\boldsymbol\Sigma_k)$ by specifying $\boldsymbol\Sigma_k \sim \text{IW}(\mathbf{V}_{0k},\nu_{0k})$ and $\boldsymbol\beta_k|\boldsymbol\Sigma_k \sim \text{N}_{Jp}(\mathbf{b}_k,\mathbf{I}_p \otimes \boldsymbol\Sigma_k)$. We assign the skewness coefficients $\boldsymbol\psi_k$ a conjugate $\text{N}_J(\mathbf{m}_k,\mathbf{P}_k)$ prior. However, the updates of $\boldsymbol\beta_k$ and $\boldsymbol\psi_k$ can be combined into one step by defining the $(Jp + J) \times 1$ vector $\boldsymbol\beta^*_k = (\boldsymbol\beta_k,\boldsymbol\psi_k)^T$ for which we assume a $\text{N}_{Jp+J}(\mathbf{b}^*_k,\mathbf{I}_{(p+1)} \otimes \boldsymbol\Sigma_k)$ prior. For the multinomial logit model component, the regression parameters $\boldsymbol\delta_k$ are assigned a $\text{N}_r(\mathbf{d}_k, \mathbf{S}_k)$ prior for $k = 1,...,K-1$, which is conditionally conjugate as described in Section (\textbf{what section}).

We allow the normal-inverse-Wishart and multinomial hyperparameters to vary across clusters, though they may be shared across clusters in practice. An advantage of allowing for cluster-specific prior parameters is that \textit{a priori} knowledge of motor development trends can be incorporated into certain clusters while allowing the priors for other clusters to be less informative. Additionally, prior information regarding the effect of certain covariates on cluster membership can be incorporated in to the model by choosing informative values for $\mathbf{d}_k \ \text{and} \ \mathbf{S}_k$

@@

\paragraph{\textbf{Step 2:} Update of MSN Regression Parameters} We begin the update of MSN regression parameters by updating $t_i$, the truncated Normal random effect used in the stochastic representation of $\mathbf{y}_i$ given in equation \ref{eq:msnreg}. For cluster $k$, compute $A_k = (1 + \boldsymbol\psi_k^T \boldsymbol\Sigma^{-1}_k\boldsymbol
\psi_k)^{-1}$ according to current values of $\boldsymbol\psi_k$ and $\boldsymbol\Sigma^{-1}_k$. Now, for $i = 1,...,n_k$, where $n_k$ is the number of members of cluster $k$ according to the current values of ${z}_1,...,{z}_n$, compute $a_i = A_k \boldsymbol\psi_k^T \boldsymbol\Sigma^{-1}_k(\mathbf{y}_i - \boldsymbol\zeta_{ik})$. Finally, update draw $t_i$ from $\text{N}_{[0,\infty)}(a_i, \mathbf{A}_k)$. \textbf{Derivations in FS-P 2010 supplement}.

The remaining MSN regression parameters are updated from their full conditionals as follows. For cluster $k$, we update $\boldsymbol\Sigma_k$ from $\text{IW}(\nu_k,\mathbf{V}_k)$, where $\nu_k = \nu_{0k} + n_k$ and 
\begin{eqnarray}
	\mathbf{V}_k &=&  (\mathbf{Y}-\mathbf{X}^*_k \mathbf{B}^*_k)^T (\mathbf{Y}_k - \mathbf{X}^*_k \mathbf{B}^*_k)\nonumber \\
	 &+& (\mathbf{B}_k^* - \mathbf{B}_{0,k})^T \mathbf{I}_{p+1}(\mathbf{B}^*_k - \mathbf{B}_{0,k}) + \mathbf{V}_{0,k}. \nonumber
\end{eqnarray}
We then make use of the Matrix Normal representation introduced in Section 3.2 to draw $\mathbb{B}^*_k$ from $\text{MatNorm}_{p+1,J}(\mathbf{B}_k^*,\mathbf{L}_k^{-1},\boldsymbol\Sigma_k)$
\paragraph{\textbf{Step 3:}P\'olya--Gamma Data Augmentation for $z_i$} The sampler concludes by updating the latent cluster indicators $z_i$ $(i=1,\ldots,n)$ from its multinomial logit full conditional. To facilitate sampling, we adopt an efficient data-augmentation approach introduced by Polson \textit{et al.} (2013), which expresses the inverse-logit function as a mixture P\'olya--Gamma densities. By using P\'olya--Gamma data augmentation for the multinomial model (\textbf{cite}), we obtain a P\'olya--Gamma mixture of experts model, a computationally efficient way to model edge weights (\textbf{cite}). A random variable $w$ is said to follow a P\'olya--Gamma distribution with parameters $b > 0$ and $c \in {\rm I\!R}$ if
\begin{equation}
w \sim \text{PG}(b,c) \stackrel{d}{=} \frac{1}{2\pi^2}\sum_{s=1}^{\infty}\frac{g_s}{(s-1/2)^2 + c^2/(4\pi^2)}, \label{eq:pg1}
\end{equation}
where $g_s \stackrel{iid}{\sim} \text{Ga}(b,1)$ for $s = 1,...,\infty$ . Polson \textit{et al.} (2013) establish that for the $\text{PG}(b,c)$ density, and for $a,\eta \in {\rm I\!R}$,

\begin{equation}
\frac{(\text{e}^{\eta})^a}{(1 + \text{e}^{\eta})^b} = 2^{-b}\text{e}^{\kappa \eta} \int_{0}^{\infty} \text{e}^{-w\eta^2/2}p(w|b,c = 0)dw. \label{eq:pg2}
\end{equation}
where $\kappa = a - b/2$. Polson \textit{et al.} also show that the conditional distribution $p(w|b,c)$ results from an ``exponential tilting'' of the $\text{PG}(b,0)$ density, thus

\begin{equation}
	p(w|b,c) = \frac{\text{e}^{-c^2w/2}p(w|b,0)}{E_w[\text{e}^{-c^2w/2}]} = \frac{\text{e}^{-c^2w/2}p(w|b,0)}{\int_0^\infty \text{e}^{-c^2w/2}p(w|b,0)dw}. \label{eq:pg3}
\end{equation}

We can use the quantities to re-express the full conditionals for $\boldsymbol\delta_k$ as
\begin{eqnarray}
	p(\boldsymbol\delta_k|\mathbf{Z},\boldsymbol\delta_{h \ne k}) &\propto& p(\boldsymbol\delta_k) \prod_{i = 1}^{n} \left (\frac{\text{e}^{\eta_{ik}}}{1 + \text{e}^{\eta_{ik}}} \right )^{U_{ik}} \left (\frac{1}{1 + \text{e}^{\eta_{ik}}} \right )^{1-U_{ik}} \nonumber\\ &=& p(\boldsymbol\delta_k) \prod_{i = 1}^n \frac{(\text{e}^{\eta_{ik}})^{U_{ik}}}{1 + \text{e}^{\eta_{ik}}} \label{eq:pglogit}
\end{eqnarray}
which we note is essentially a logistic regression likelihood. We thus apply this P\'olya--Gamma data augmentation scheme to update each $\boldsymbol\delta_k$ ($k = 1,...,K-1$) one at a time based on the binary indicators $U_{ik}$.

>>>>

%  ALWAYS USE THE referee OPTION WITH PAPERS SUBMITTED TO BIOMETRICS!!!
%  You can see what your paper would look like typeset by removing
%  the referee option.  Because the typeset version will be in two
%  columns, however, some of your equations may be too long. DO NOT
%  use the \longequation option discussed in the user guide!!!  This option
%  is reserved ONLY for equations that are impossible to split across 
%  multiple lines; e.g., a very wide matrix.  Instead, type your equations 
%  so that they stay in one column and are split across several lines, 
%  as are almost all equations in the journal.  Use a recent version of the
%  journal as a guide. 
%  
\documentclass[useAMS,referee]{biom}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{booktabs}
\usepackage{breqn}
\usepackage{algorithm}
\usepackage{algcompatible}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{dsfont}
\usepackage{dutchcal}
\usepackage{amsfonts}

@@

\begin{abstract}
In studies of infant motor development, a crucial research goal is to identify latent clusters of infants that experience delayed development, as this is a known risk factor for adverse outcomes later in life. However, there are a number of statistical challenges in modeling infant development: the data are typically skewed, exhibit intermittent missingness, and are highly correlated across the repeated measurements collected during infancy. Using data from the Nurture study, a cohort of over 600 mother-infant pairs followed from pregnancy to 12 months postpartum, we develop a flexible Bayesian latent class model for the analysis infant motor development. Our model has a number of attractive features. First, we adopt the multivariate skew normal distribution with cluster-specific parameters that accommodate the inherent correlation and skewness in the data. Second, we model the cluster membership probabilities using a novel P\'olya-Gamma data-augmentation scheme, thereby improving predictions of the cluster membership allocations. Lastly, we impute missing responses under missing at random assumption by drawing from appropriate conditional skew normal distributions. Bayesian inference is achieved through straightforward Gibbs sampling, and can be carried out in available software such as R.  Through simulation studies, we show that the proposed model yields improved inferences over models that ignore skewness. In addition, our imputation method yields improvements compared to conventional missing data methods, including multiple imputation and complete or available case analysis. When applied to Nurture data, we identified two distinct development clusters: one characterized by delayed “U-shaped” development and a higher percentage of male infants and another characterized by more steady development and a lower percentage of males. The clusters also differed in terms of key demographic variables, such as infant race and maternal pre-pregnancy body mass index. These findings can aid investigators in targeting interventions during this critical early-life developmental window.
\end{abstract}

@@

To facilitate sampling, we adopt an efficient data-augmentation approach introduced by Polson \textit{et al.} (2013), which expresses the inverse-logit function as a mixture P\'olya--Gamma densities. By using P\'olya--Gamma data augmentation for the multinomial model (\textbf{cite}), we obtain a P\'olya--Gamma mixture of experts model, a computationally efficient way to model edge weights (\textbf{cite}). A random variable $\mathcal{w}$ is said to follow a P\'olya--Gamma distribution with parameters $b > 0$ and $c \in {\rm I\!R}$ if
\begin{equation}
\mathcal{w} \sim \text{PG}(b,c) \stackrel{d}{=} \frac{1}{2\pi^2}\sum_{s=1}^{\infty}\frac{g_s}{(s-1/2)^2 + c^2/(4\pi^2)}, \label{eq:pg1}
\end{equation}
where $g_s \stackrel{iid}{\sim} \text{Ga}(b,1)$ for $s = 1,...,\infty$ . Polson \textit{et al.} (2013) establish that for the $\text{PG}(b,c)$ density, and for $a,\eta \in {\rm I\!R}$,

\begin{equation}
\frac{(\text{e}^{\eta})^a}{(1 + \text{e}^{\eta})^b} = 2^{-b}\text{e}^{\kappa \eta} \int_{0}^{\infty} \text{e}^{-\mathcal{w}\eta^2/2}p(\mathcal{w}|b,c = 0)d\mathcal{w}. \label{eq:pg2}
\end{equation}
where $\kappa = a - b/2$. Polson \textit{et al.} also show that the conditional distribution $p(\mathcal{w}|b,c)$ results from an ``exponential tilting'' of the $\text{PG}(b,0)$ density, thus

\begin{equation}
	p(\mathcal{w}|b,c) = \frac{\text{e}^{-c^2\mathcal{w}/2}p(\mathcal{w}|b,0)}{E_{\mathcal{w}}[\text{e}^{-c^2\mathcal{w}/2}]} = \frac{\text{e}^{-c^2\mathcal{w}/2}p(\mathcal{w}|b,0)}{\int_0^\infty \text{e}^{-c^2\mathcal{w}/2}p(\mathcal{w}|b,0)d\mathcal{w}}. \label{eq:pg3}
\end{equation}

We can use the quantities to re-express the full conditionals for $\boldsymbol\delta_k$ as
\begin{eqnarray}
	p(\boldsymbol\delta_k|\mathbf{Z},\boldsymbol\delta_{h \ne k}) &\propto& p(\boldsymbol\delta_k) \prod_{i = 1}^{n} \left (\frac{\text{e}^{\eta_{ik}}}{1 + \text{e}^{\eta_{ik}}} \right )^{U_{ik}} \left (\frac{1}{1 + \text{e}^{\eta_{ik}}} \right )^{1-U_{ik}} \nonumber\\ &=& p(\boldsymbol\delta_k) \prod_{i = 1}^n \frac{(\text{e}^{\eta_{ik}})^{U_{ik}}}{1 + \text{e}^{\eta_{ik}}} \label{eq:pglogit}
\end{eqnarray}
which we note is essentially a logistic regression likelihood. We thus apply this P\'olya--Gamma data augmentation scheme from Polson et al. (2013) to update each $\boldsymbol\delta_k$ ($k = 1,...,K-1$) one at a time based on the binary indicators $U_{ik}$.

@@

\subsubsection{Prior Specification}
We adopt a fully Bayesian inferential approach and assign prior distributions to all model parameters. Conveniently, all parameters admit conditionally conjugate priors, which greatly improves posterior computation via a data-augmented Gibbs sampler. For the MSN model component, we adopt a conditionally independent prior structure for $\boldsymbol\beta_k$ and $\boldsymbol\Sigma_k$, where $p(\boldsymbol\beta_k,\boldsymbol\Sigma_k) = p(\boldsymbol\Sigma_k)p(\boldsymbol\beta_k|\boldsymbol\Sigma_k)$. We choose the normal-inverse-Wishart distribution for $p(\boldsymbol\beta_k,\boldsymbol\Sigma_k)$ by specifying $\boldsymbol\Sigma_k \sim \text{IW}(\mathbf{V}_{0k},\nu_{0k})$ and $\boldsymbol\beta_k|\boldsymbol\Sigma_k \sim \text{N}_{Jp}(\mathbf{b}_k,\mathbf{I}_p \otimes \boldsymbol\Sigma_k)$. We assign the skewness coefficients $\boldsymbol\psi_k$ a conjugate $\text{N}_J(\mathbf{m}_k,\mathbf{P}_k)$ prior. In practice, the updates of $\boldsymbol\beta_k$ and $\boldsymbol\psi_k$ can be combined into one step by defining the $(Jp + J) \times 1$ vector $\boldsymbol\beta^*_k = (\boldsymbol\beta_k,\boldsymbol\psi_k)^T$ for which we assume a $\text{N}_{Jp+J}(\mathbf{b}^*_k,\mathbf{I}_{(p+1)} \otimes \boldsymbol\Sigma_k)$ prior.

To make use of the Matrix Normal representation introduced previously in Section (\textbf{what section}), we define the matrix of regression parameters $\mathbb{B}^*_k$, where $\text{vec}(\mathbb{B}^*_k) = \boldsymbol\beta^*_k$. We assign $\mathbb{B}^*_k|\boldsymbol\Sigma_k$ a $\text{MatNorm}(\mathbf{B}^*_{0k},\mathbf{I}_{p+1},\boldsymbol\Sigma_k)$, where $\mathbf{B}^*_{0k}$ is a matrix of location parameters such that $\text{vec}(\mathbf{B}^*_{0k}) = \mathbf{b}^*_k$, $\mathbf{I}_{p+1}$ is the identity matrix of dimensions $(p+1)\times(p+1)$, and $\boldsymbol\Sigma_k$ is the model error. This prior structure allows for convinient Matrix Normal updates of the MSN regression parameters as described in Section (\textbf{what section}).

For the multinomial logit model component, the regression parameters $\boldsymbol\delta_k = (\delta_{k1},...,\delta_{kr})$ are assigned a $\text{N}_r(\mathbf{d}_{0k}, \mathbf{S}_{0k})$ prior for $k = 1,...,K-1$, which is conditionally conjugate as described in Section (\textbf{what section}). We allow the normal-inverse-Wishart and multinomial hyperparameters to vary across clusters, though they may be shared across clusters in practice. An advantage of allowing for cluster-specific prior parameters is that \textit{a priori} knowledge of motor development trends can be incorporated into certain clusters while allowing the priors for other clusters to be less informative. Additionally, prior information regarding the effect of certain covariates on cluster membership can be incorporated in to the model by choosing informative values for $\mathbf{d}_{0k} \ \text{and} \ \mathbf{S}_{0k}$

@@

\paragraph{\textbf{Step 2:} Update of MSN Regression Parameters} We begin the update of MSN regression parameters by updating $t_i$, the truncated Normal random effect used in the stochastic representation of $\mathbf{y}_i$ given in equation \ref{eq:msnreg}. For cluster $k$, compute $A_k = (1 + \boldsymbol\psi_k^T \boldsymbol\Sigma^{-1}_k\boldsymbol
\psi_k)^{-1}$ according to current values of $\boldsymbol\psi_k$ and $\boldsymbol\Sigma_k$. Now, for $i = 1,...,n_k$, where $n_k$ is the number of members of cluster $k$ according to the current cluster labeling ${z}_1,...,{z}_n$, compute $a_i = A_k \boldsymbol\psi_k^T \boldsymbol\Sigma^{-1}_k(\mathbf{y}_i - \boldsymbol\zeta_{ik})$. Finally, update $t_i$ from $\text{N}_{[0,\infty)}(a_i, \mathbf{A}_k)$ (\textbf{put derivations in supplement}).  Repeat these updates for $k = 1,...,K$

The remaining MSN regression parameters are updated from their full conditionals as follows. For each cluster $k$ ($k = 1,...,K$) we update $\boldsymbol\Sigma_k$ from $\text{IW}(\nu_k,\mathbf{V}_k)$, where $\nu_k = \nu_{0k} + n_k$ and\begin{eqnarray}
	\mathbf{V}_k &=&  (\mathbf{Y}-\mathbf{X}^*_k \mathbf{B}^*_k)^T (\mathbf{Y}_k - \mathbf{X}^*_k \mathbf{B}^*_k)\nonumber \\
	 &+& (\mathbf{B}_k^* - \mathbf{B}^*_{0k})^T \mathbf{I}_{p+1}(\mathbf{B}^*_k - \mathbf{B}^*_{0k}) + \mathbf{V}_{0k}. \nonumber
\end{eqnarray}We then make use of the Matrix Normal representation introduced in Section 3.2 to draw $\mathbb{B}^*_k$ from $\text{MatNorm}_{p+1,J}(\mathbf{B}_k^*,\mathbf{L}_k^{-1},\boldsymbol\Sigma_k)$, where $\text{vec}(\mathbb{B}^*_k) = \boldsymbol\beta^*_k = (\beta_{k11},...,\beta_{kJp},\psi_{k1},...,\psi_{kJ})^T$ and
\begin{eqnarray}
	\mathbf{B}^*_k &=& (\mathbf{X}^{*T}_k \mathbf{X}^*_k + \mathbf{I}_{p+1})^{-1} (\mathbf{X}^{*T}_k \mathbf{Y}_k + \mathbf{I}_{p+1} \mathbf{B}_{0k}) \nonumber \\
	\mathbf{L}^*_k &=& \mathbf{X}^{*T}_k \mathbf{X}^*_k + \mathbf{I}_{p+1}. \nonumber
\end{eqnarray}

\paragraph{\textbf{Step 3:}P\'olya--Gamma Data Augmentation for $z_i$} The sampler concludes with updates of the multinomial regression parameters $\boldsymbol\delta_k$, for $k = 1,...,K-1$, followed by updates of each latent cluster indicator $z_i$ $(i=1,\ldots,n)$ from its multinomial logit full conditional. First, we define $U_{ik} = {1}_{z_i = k}$ for $i = 1,...,n$ and $k = 1,...,K-1$. Next, we update $\mathcal{w}_{ik}$ from a $\text{PG}(1,\eta_{ik})$ density, where $\eta_{ik} = \mathbf{w}_i^T \boldsymbol\delta_k - {c}_{ik}$, and ${c}_{ik} = \log \sum_{h \ne k} \text{e}^{\mathbf{w}_i^T \boldsymbol\delta_{h}}$. Next, define $\gamma_{ik} = \frac{u_{ik} - 1/2}{\mathcal{w}_{ik}}$ and let $\boldsymbol\gamma_k = (\gamma_{1k},...,\gamma_{nk})^T$. Finally, for $k = 1,...,K-1$, update $\boldsymbol\delta_k$ from a $\text{N}_r(\mathbf{d}_k,\mathbf{S}_k)$, where $\mathbf{S}_k = (\mathbf{S}_{0k} + \mathbf{W}^T \mathcal{W}_k \mathbf{W})^{-1}$, $\mathcal{W}_k = \text{Diag}(\mathcal{w}_{1k},...,\mathcal{w}_{nk})$,  $\mathbf{W} =  (\mathbf{w}^T_1,...,\mathbf{w}^T_n)^T$, and $\mathbf{d}_k = \mathbf{S}_k (\mathbf{S}_{0k}\mathbf{d}_{0k} + \mathbf{W}^T \mathcal{W}_k \boldsymbol\gamma_k)$.

Lastly, we update $z_1,...,z_n$ by first computing 
$$\pi_{ik} = \frac{\text{e}^{\eta_{ik}}}{1 + \sum_{h=1}^{K-1} \text{e}^{\eta_{ih}}},$$ 
where $\eta_{ik} = \mathbf{w}_i\boldsymbol\delta_k$ for $i = 1,...n$ and $k = 1,...,K-1$. We also compute according to the multivariate Normal density of $\mathbf{y}_i|t_i$ the probability $P(\mathbf{y}_i|\boldsymbol\zeta^*_{ki},\boldsymbol\Sigma_k)$, where $\boldsymbol\zeta_{ki} = \mathbf{x}_i^*\boldsymbol\beta^*_k$. We use these quantities to compute $\boldsymbol\varrho_{i} = (\varrho_{1i},...,\varrho_{Ki})$, where  
$$\varrho_{ik} = P(z_i = k) = \frac{\pi_{ik}P(\mathbf{y}_i|\boldsymbol\zeta^*_{ki},\boldsymbol\Sigma_k)}{\sum_{h = 1}^{K} \pi_{ih}P(\mathbf{y}_i|\boldsymbol\zeta^*_{hi},\boldsymbol\Sigma_h)}$$.
The cluster labels $z_i$ are updated from a $\text{Categorical}(\boldsymbol\varrho_i)$ density for $i = 1,...n$, thus concluding the Gibbs sampler.
